\chapter{Milestone reports}
\label{app:Milestone-Reports}
In diesem Kapitel werden die einzelnen Berichte der Meilensteine aufgef체hrt. Diese sollen Aufschluss 체ber den Stand des
Projektes w채hrend der Umsetzung geben.

\section{Meilensteinbericht M1 vom 26. September 2019}

\subsection{Aktueller Stand bei Meilenstein}

\subsection{Ausblick zum n채chsten Meilenstein}

\chapter{Research}
\label{app:Research}
Within this chapter of the thesis, there are summaries of the papers from the research. The summaries should highlight the most important parts of the resource.

\section{Dataset}
\label{sec:Research-Dataset}

\subsection{Resources}
\begin{itemize}
    \item \cite{dekkers_sins_2017}
    \item \cite{dekkers_dcase_2018}
\end{itemize}

\section{DCASE 2018 Challenge - Task 5: Monitoring of domestic activities based on multi-channel acoustics \footfullcite{dekkers_sins_2017}}
This website contains all the necessary information about the challenge from the IEEE AASP Challenge on \gls{DCASE} 2018. The challenge finished in 2018, and the results, as well as the full dataset, was published. The main goal of the challenge was to classify multi-channel audio segments into predefined classes. These predefined classes are daily activities performed in a typical household.
\begin{itemize}
    \item TODO
\end{itemize}

\chapter{Work journal}
\label{ch:Work-Journal}

\landscapevalues
\clearpage

\begin{longtable}{| p{.10\textwidth} | p{.20\textwidth} | p{.50\textwidth} | p{.10\textwidth} |} 
	\caption{Work Journal}
	\label{tab:Work-Journal} \\
    \hline
    \textbf{Date} &
    \textbf{Task} &
    \textbf{Details} &
    \textbf{No. hours} \\
    \hline
    \multicolumn{4}{|l|}{\textbf{General}} \\
    \hline
    17.02.2020 & Preparation for Kick-Off Meeting & 
        \begin{minipage}{5in}
        \vskip 4pt
        \begin{itemize}
        \setlength\itemsep{0em}
        \item thesis description read carefully again
        \item questions of unclear matters
        \end{itemize}
        \vskip 4pt
        \end{minipage}
        & 1h  \\
    \hline
    17.02.2020 & Kick-Off Meeting & 
        \begin{minipage}{5in}
        \vskip 4pt
        \begin{itemize}
        \setlength\itemsep{0em}
        \item discussed different topics which are important for the implementation of the project
        \end{itemize}
        \vskip 4pt
        \end{minipage}
        & 1h 30min  \\
    \hline
    \multicolumn{4}{|l|}{\textbf{Documentation}} \\
    \hline
    17.02.2020 & Documentation setup & 
        \begin{minipage}{5in}
        \vskip 4pt
        \begin{itemize}
        \setlength\itemsep{0em}
        \item project setup
        \item latex document setup
        \item German transcribed to English
        \item built default documentation structure
        \end{itemize}
        \vskip 4pt
        \end{minipage}
        & 2h  \\
    \hline
    19.02.2020 & Dataset documented & 
        \begin{minipage}{5in}
        \vskip 4pt
        \begin{itemize}
        \setlength\itemsep{0em}
        \item SINS Database
        \item DCASE Task dataset
        \end{itemize}
        \vskip 4pt
        \end{minipage}
        & 3h  \\
    \hline
    24.02.2020 & Dataset documented finished & 
        \begin{minipage}{5in}
        \vskip 4pt
        \begin{itemize}
        \setlength\itemsep{0em}
        \item Created table of the recorded activities in the \gls{SINS} database
        \item Reread section and corrected
        \end{itemize}
        \vskip 4pt
        \end{minipage}
        & 1h  \\
    \hline
    \multicolumn{4}{|l|}{\textbf{Research}} \\
    \hline
    17.02.2020 & Research Dataset & 
        \begin{minipage}{5in}
        \vskip 4pt
        \begin{itemize}
        \setlength\itemsep{0em}
        \item finished with DCASE - Challenge description
        \item started with SINS Database Paper
        \end{itemize}
        \vskip 4pt
        \end{minipage}
        & 2h 30min  \\
    \hline
    21.02.2020 & Audio processing research & 
        \begin{minipage}{5in}
        \vskip 4pt
        \begin{itemize}
        \setlength\itemsep{0em}
        \item \gls{FT}
        \item \gls{FFT}
        \item \gls{DFT}
        \item Spectrogram
        \item started with related work documentation
        \end{itemize}
        \vskip 4pt
        \end{minipage}
        & 5h  \\
    \hline
\end{longtable}

\clearpage
\defaultpagestyle
